CS222 Project Proposal: Task-Specific Network Fusion through CDRP Model Decomposition and Assembly

### 2020-01-06 proposal/proposal.tex
update proposal figure and some notation

>>>>

\newpage
\begin{itemize}
	\item $L$ class labels, denoted $\{l_j\}$
	\item $N$ subclasses in total \begin{itemize}
		\item $M$ target subclasses, denoted $\mathcal{A} = \{A_i\}$
		\item $N-M$ dummy subclasses (with irrelevant class labels), denoted $\bar{\mathcal{A}} = \{A_i\}$
	\end{itemize}
	\item $g(A_i) := l_j$ the partial map from $A_i$ to class label $l_j$
	\item $K$ classifiers, denoted $\mathcal{D} = \{d_j\}$
	\item $f(A_i, d_j) := 0, 1$ the classifier certificate that $A_i$ is classified positive in classifier $d_j$
	\item $score(d_j)$ the performance of classifier $d_j$
	\item $k$ the maximum number of classifier to use
\end{itemize}

\begin{itemize}
	\item $D \subset \mathcal{D}$ a set of $m$ classifiers \textit{covering} all $M$ target subclasses s.t. $m < k$
	\item $score(D)$ the overall performance of the classifier set
\end{itemize}

We define the concept of \textit{covering} as follows.
\begin{definition}
	A set of classifiers covers $M$ target subclasses iff. given any sample, the joint classifier can determine whether it \textit{solely} belongs to \begin{enumerate}
		\item a subset (with consistent labels) of the $M$ target subclasses, or,
		\item the rest dummy subclasses $\bar{\mathcal{A}}$.
	\end{enumerate}
\end{definition}
